---
title: "2022 Football Season Statistical Analysis"
author: "Justin Carter"
date: "3/10/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Dataset, check variable types:



```{r}
library(readr)
library(tidyverse)
library(randomForest)
library(caret)
library(dplyr)

#original dataset was called the variable "football"

Week2 = read_csv("Finalized_Week2_Dataset_2022.csv")
Week3 = read_csv("Finalized_Week3_Dataset_2022.csv")
Week4 = read_csv("Finalized_Week4_Dataset_2022.csv")
Week5 = read_csv("Finalized_Week5_Dataset_2022.csv")
Week6 = read_csv("Finalized_Week6_Dataset_2022.csv")
Week7 = read_csv("Finalized_Week7_Dataset_2022.csv")
Week8 = read_csv("Finalized_Week8_Dataset_2022.csv")
Week9 = read_csv("Finalized_Week9_Dataset_2022.csv")
Week10 = read_csv("Finalized_Week10_Dataset_2022.csv")
Week11 = read_csv("Finalized_Week11_Dataset_2022.csv")
Week12 = read_csv("Finalized_Week12_Dataset_2022.csv")
Week13 = read_csv("Finalized_Week13_Dataset_2022.csv")
Week14 = read_csv("Finalized_Week14_Dataset_2022.csv")
Bowls1 = read_csv("Finalized_Bowls1_Dataset_2022.csv")
Bowls2 = read_csv("Finalized_Bowls2_Dataset_2022.csv")
Week18 = read_csv("Finalized_Week18_Dataset_2022.csv")
Combined = read_csv("Finalized_Combined_Dataset_2022.csv")



```

#Week 2
Modify Week 2 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week2 <- separate(data=Week2, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week2 <- Week2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week2 <- separate(data=Week2, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week2 <- Week2 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week2 <- separate(data=Week2, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week2 <- Week2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week2 <- separate(data=Week2, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week2 <- Week2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week2 <- Week2 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week2 <- Week2 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week2 <- Week2 %>%
  select(-(`...1`))

```



Make Random Forest Model to Predict Game Winner for Week 2
```{r}
 set.seed(1)
 data_used = Week2
 
 ctrl = trainControl(method= "cv", number=10)
 Week2_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week2_rf_caret

 
 Week2_rf_caret$finalModel
 
 varImp(Week2_rf_caret)
 


```



#Week 3
Modify Week 3 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week3 <- separate(data=Week3, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week3 <- Week3 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week3 <- separate(data=Week3, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week3 <- Week3 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week3 <- separate(data=Week3, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week3 <- Week3 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week3 <- separate(data=Week3, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week3 <- Week3 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week3 <- Week3 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week3 <- Week3 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week3 <- Week3 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 3
```{r}
 set.seed(1)
 data_used = Week3
 
 ctrl = trainControl(method= "cv", number=10)
 Week3_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week3_rf_caret

 
 Week3_rf_caret$finalModel
 
 varImp(Week3_rf_caret)
 


```


#Week 4
Modify Week 4 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week4 <- separate(data=Week4, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week4 <- Week4 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week4 <- separate(data=Week4, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week4 <- Week4 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week4 <- separate(data=Week4, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week4 <- Week4 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week4 <- separate(data=Week4, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week4 <- Week4 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week4 <- Week4 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week4 <- Week4 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week4 <- Week4 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 4
```{r}
 set.seed(1)
 data_used = Week4
 
 ctrl = trainControl(method= "cv", number=10)
 Week4_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week4_rf_caret

 
 Week4_rf_caret$finalModel
 
 varImp(Week4_rf_caret)
 

 

```


#Week 5

Modify Week 5 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week5 <- separate(data=Week5, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week5 <- Week5 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week5 <- separate(data=Week5, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week5 <- Week5 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week5 <- separate(data=Week5, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week5 <- Week5 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week5 <- separate(data=Week5, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week5 <- Week5 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week5 <- Week5 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week5 <- Week5 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week5 <- Week5 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 5
```{r}
 set.seed(1)
 data_used = Week5
 
 ctrl = trainControl(method= "cv", number=10)
 Week5_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week5_rf_caret

 
 Week5_rf_caret$finalModel
 
 varImp(Week5_rf_caret)
 

 

```



#Week 6

Modify Week 6 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week6 <- separate(data=Week6, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week6 <- Week6 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week6 <- separate(data=Week6, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week6 <- Week6 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week6 <- separate(data=Week6, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week6 <- Week6 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week6 <- separate(data=Week6, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week6 <- Week6 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week6 <- Week6 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week6 <- Week6 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week6 <- Week6 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 6
```{r}
 set.seed(1)
 data_used = Week6
 
 ctrl = trainControl(method= "cv", number=10)
 Week6_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week6_rf_caret

 
 Week6_rf_caret$finalModel
 
 varImp(Week6_rf_caret)
 

 

```



#Week 7
Modify Week 7 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week7 <- separate(data=Week7, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week7 <- Week7 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week7 <- separate(data=Week7, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week7 <- Week7 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week7 <- separate(data=Week7, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week7 <- Week7 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week7 <- separate(data=Week7, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week7 <- Week7 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week7 <- Week7 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week7 <- Week7 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week7 <- Week7 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 7
```{r}
 set.seed(1)
 data_used = Week7
 
 ctrl = trainControl(method= "cv", number=10)
 Week7_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week7_rf_caret

 
 Week7_rf_caret$finalModel
 
 varImp(Week7_rf_caret)
 

```


#Week 8
Modify Week 8 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week8 <- separate(data=Week8, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week8 <- Week8 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week8 <- separate(data=Week8, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week8 <- Week8 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week8 <- separate(data=Week8, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week8 <- Week8 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week8 <- separate(data=Week8, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week8 <- Week8 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week8 <- Week8 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week8 <- Week8 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week8 <- Week8 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 8
```{r}
 set.seed(1)
 data_used = Week8
 
 ctrl = trainControl(method= "cv", number=10)
 Week8_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week8_rf_caret

 
 Week8_rf_caret$finalModel
 
 varImp(Week8_rf_caret)
 

```



#Week 9
Modify Week 9 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week9 <- separate(data=Week9, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week9 <- Week9 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week9 <- separate(data=Week9, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week9 <- Week9 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week9 <- separate(data=Week9, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week9 <- Week9 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week9 <- separate(data=Week9, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week9 <- Week9 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week9 <- Week9 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week9 <- Week9 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week9 <- Week9 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 9
```{r}
 set.seed(1)
 data_used = Week9
 
 ctrl = trainControl(method= "cv", number=10)
 Week9_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week9_rf_caret

 
 Week9_rf_caret$finalModel
 
 varImp(Week9_rf_caret)
 

 

```



#Week 10
Modify Week 10 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week10 <- separate(data=Week10, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week10 <- Week10 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week10 <- separate(data=Week10, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week10 <- Week10 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week10 <- separate(data=Week10, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week10 <- Week10 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week10 <- separate(data=Week10, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week10 <- Week10 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week10 <- Week10 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week10 <- Week10 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week10 <- Week10 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 10
```{r}
 set.seed(1)
 data_used = Week10
 
 ctrl = trainControl(method= "cv", number=10)
 Week10_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week10_rf_caret

 
 Week10_rf_caret$finalModel
 
 varImp(Week10_rf_caret)
 

```



#Week 11
Modify Week 11 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week11 <- separate(data=Week11, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week11 <- Week11 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week11 <- separate(data=Week11, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week11 <- Week11 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week11 <- separate(data=Week11, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week11 <- Week11 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week11 <- separate(data=Week11, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week11 <- Week11 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week11 <- Week11 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week11 <- Week11 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week11 <- Week11 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 11
```{r}
 set.seed(1)
 data_used = Week11
 
 ctrl = trainControl(method= "cv", number=10)
 Week11_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week11_rf_caret

 
 Week11_rf_caret$finalModel
 
 varImp(Week11_rf_caret)
 

 

```



#Week 12
Modify Week 12 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week12 <- separate(data=Week12, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week12 <- Week12 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week12 <- separate(data=Week12, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week12 <- Week12 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week12 <- separate(data=Week12, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week12 <- Week12 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week12 <- separate(data=Week12, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week12 <- Week12 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week12 <- Week12 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week12 <- Week12 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week12 <- Week12 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 12
```{r}
 set.seed(1)
 data_used = Week12
 
 ctrl = trainControl(method= "cv", number=10)
 Week12_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week12_rf_caret

 
 Week12_rf_caret$finalModel
 
 varImp(Week12_rf_caret)
 


```


#Week 13
Modify Week 13 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Week13 <- separate(data=Week13, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week13 <- Week13 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Week13 <- separate(data=Week13, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Week13 <- Week13 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Week13 <- separate(data=Week13, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week13 <- Week13 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Week13 <- separate(data=Week13, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Week13 <- Week13 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Week13 <- Week13 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Week13 <- Week13 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Week13 <- Week13 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Week 13
```{r}
 set.seed(1)
 data_used = Week13
 
 ctrl = trainControl(method= "cv", number=10)
 Week13_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Week13_rf_caret

 
 Week13_rf_caret$finalModel
 
 varImp(Week13_rf_caret)
 

```


#Bowls 1
Modify Bowls 1 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Bowls1 <- separate(data=Bowls1, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls1 <- Bowls1 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Bowls1 <- separate(data=Bowls1, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Bowls1 <- Bowls1 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Bowls1 <- separate(data=Bowls1, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls1 <- Bowls1 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Bowls1 <- separate(data=Bowls1, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls1 <- Bowls1 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Bowls1 <- Bowls1 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Bowls1 <- Bowls1 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Bowls1 <- Bowls1 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Bowls 1
```{r}
 set.seed(1)
 data_used = Bowls1
 
 ctrl = trainControl(method= "cv", number=10)
 Bowls1_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Bowls1_rf_caret

 
 Bowls1_rf_caret$finalModel
 
 varImp(Bowls1_rf_caret)
 

```



#Bowls 2
Modify Bowls 2 Dataset in Preparation for Analysis
```{r}

#Convert Away_Team_Time_Of_Possession_TOP to seconds
Bowls2 <- separate(data=Bowls2, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls2 <- Bowls2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Bowls2 <- separate(data=Bowls2, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Bowls2 <- Bowls2 %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Bowls2 <- separate(data=Bowls2, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls2 <- Bowls2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Bowls2 <- separate(data=Bowls2, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Bowls2 <- Bowls2 %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Bowls2 <- Bowls2 %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Bowls2 <- Bowls2 %>%
  mutate(Winner = as.factor(Winner))

#Drop redundant ...1 Column
Bowls2 <- Bowls2 %>%
  select(-(`...1`))



```



Make Random Forest Model to Predict Game Winner for Bowls 2
```{r}
 set.seed(1)
 data_used = Bowls2
 
 ctrl = trainControl(method= "cv", number=10)
 Bowls2_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(18,19,20)),
              trControl = ctrl)

 Bowls2_rf_caret

 
 Bowls2_rf_caret$finalModel
 
 varImp(Bowls2_rf_caret)
 

```




#Combined Dataset
Modify Combined Dataset for Analysis Purposes
```{r}
#Convert Away_Team_Time_Of_Possession_TOP to seconds
Combined <- separate(data=Combined, col = Away_Team_Time_Of_Possession_TOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Combined <- Combined %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_TOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))



#Convert Home_Team_Time_Of_Possession_TOP to seconds
Combined <- separate(data=Combined, col = Home_Team_Time_Of_Possession_TOP, into = c("HTOP1", "HTOP2", "HTOP3"), sep =":")


Combined <- Combined %>%
  mutate(HTOP1 = as.numeric(HTOP1), HTOP2=as.numeric(HTOP2), HTOP3 = as.numeric(HTOP3), Home_Team_Time_Of_Possession_TOP = HTOP1*60 + HTOP2)%>%
  select(-c(HTOP1, HTOP2, HTOP3))


#Convert Away_Team_Time_Of_Possession_AvgTOP to seconds
Combined <- separate(data=Combined, col = Away_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Combined <- Combined %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Away_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Convert Home_Team_Tiem_Of_Possession_AvgTOP to seconds
Combined <- separate(data=Combined, col = Home_Team_Time_Of_Possession_AvgTOP, into = c("ATOP1", "ATOP2", "ATOP3"), sep =":")


Combined <- Combined %>%
  mutate(ATOP1 = as.numeric(ATOP1), ATOP2=as.numeric(ATOP2), ATOP3 = as.numeric(ATOP3), Home_Team_Time_Of_Possession_AvgTOP = ATOP1*60 + ATOP2)%>%
  select(-c(ATOP1, ATOP2, ATOP3))

#Now, drop Home_Team, Away_Team, Away_Team_3rd_Down_Conversion_Pct_W-L, and Home_Team_3rd_Down_Conversion_Pct_W-L from the dataset:

Combined <- Combined %>%
  select(-c(Home_Team, Away_Team, `Away_Team_3rd_Down_Conversion_Pct_W-L`,
            `Home_Team_3rd_Down_Conversion_Pct_W-L`))

#Convert Winner to Factor Variable

Combined <- Combined %>%
  mutate(Winner = as.factor(Winner))

#Get rid of redundant ...1 column:
Combined <- Combined %>%
  select(-...1)


```



Make Random Forest Model to Predict Game Winner for Combined Dataset
```{r}
 set.seed(1)
 Combined_index <- createDataPartition(Combined$Winner, p=.8, list=FALSE)
 Combined_train <- Combined[Combined_index,]
 Combined_test <- Combined[-Combined_index,]


 data_used = Combined_train
 

 
 
 ctrl = trainControl(method= "cv", number=10)
 Combined_rf_caret = train( Winner~.,
              data = data_used,
              method = "rf",
              tuneGrid = expand.grid(mtry = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)),
              trControl = ctrl)
 
 
Combined_rf_caret

 
Combined_rf_caret$finalModel
 
 
 #Use model on test set and get accuracy measures
 
 Combined_preds <- predict(Combined_rf_caret, newdata=Combined_test)
 conf_mat<-confusionMatrix(Combined_preds, Combined_test$Winner, positive = "1")

conf_mat

comb_var_imp <- varImp(Combined_rf_caret)
comb_var_imp
```




